%I'd like to thanks the Ghosts of Penn Students Past for providing me with such an amazing thesis template.
It would be impossible to properly thank everyone who has helped me along this journey; nevertheless I will attempt to be as thorough as possible.

First and foremost, I would like to thank my family.
My parents, Gwynne Kennedy and John DiClemente, for always believing in me and enjoying my attempts to explain what it is I am working on.
My many feline friends past and present---Stella, Lucky, Julia, Elise, Lucille, Tweedie, Ruby, and Sylvie---for keeping me warm during the winter holidays back home.
My girlfriend Amber Wright, for tolerating me these past few months and doing her best to keep me relatively sane.

Thanks to my advisor Joe Kroll for guiding me through the past six years at Penn; your advice both in physics and in life has been invaluable to my growth as a physicist and a person.
Additional thanks to the rest of the ATLAS faculty at Penn: Elliot Lipeles, Evelyn Thomson, and Brig Williams.
The amount of open collaboration between students and faculty irrespective of who works for whom has helped me learn so much.

I would also like to extend thanks to two important figures from before my time at Penn.
First, to Gardner Friedlander, my high school physics teacher who first got me interested in the subject.
You were the first to show me how I could use a pen and paper to predict events in real life---a fascination of mine that has continued into my work here, just with much harder math and on a more fundamental scale.
Second, my undergraduate research advisor, Al Goshaw, at Duke University.
You gave a college freshman who thought particle physics was ``pretty neat'' the opportunity to do meaningful research with one of the leading collaborations in the field.
Without either of you, I likely would not be in this position today.

Thanks to the members of the Inner Detector Alignment group, including but not limited to Anthony Morley for his guidance on my qualification task, and to Shih-Chieh Hsu, Pierfrancesco Butti, Matthias Danninger, Salvador Marti, and Steffen Henkelmann for numerous collaborative alignment efforts.

The entire \ssww $13\tev$ analysis group, and those with whom I worked most closely: Philip Sommer, Emily Duffield, Rustem Ospanov, Stefanie Todt, and Liqing Zhang.
Special thanks to Rustem for pushing me to find my voice in the analysis.
Thanks to my \ssww HL-LHC prospects collaborators Claire Lee and Karolos Potamiamos.

Lastly, thanks to my fellow Penn ATLAS graduate students, Bijan Haney, Joey Reichert, Khilesh Mistry, Leigh Schaefer, Bill Balunas, Christian Herwig, Elodie Resseguie, and many more, for listening to my ramblings, answering my many questions, and for countless entertaining lunchtime discussions.
