%% \chapter[htoc-titlei][hhead-titlei]{htitlei}
%% -----------------------------------------------------------------------------
\chapter[Measurement of same-sign $WW$ production at $\sqrt{s} = 13~\mathrm{TeV}$ with ATLAS][Measurement of same-sign $WW$ production at $\sqrt{s} = 13~\mathrm{TeV}$ with ATLAS]{Measurement of same-sign $WW$ production at $\sqrt{s} = 13~\mathrm{TeV}$ with ATLAS}
\label{ch:ssww13tev}
\setcounter{subsection}{0}

Production of same-sign $W$ boson pairs is a particularly interesting SM process.
When produced via vector boson scattering (VBS), \ssww is sensitive to the electroweak symmetry breaking (EWSB) mechanism as well as potential Beyond the Standard Model (BSM) physics processes.
\ssww events can be produced via electroweak-mediated (EWK) diagrams, of which VBS is a subset, or QCD-mediated diagrams. 
The biggest advantage of same-sign \ssww over other VBS processes lies in its ratio of electroweak (EWK) to QCD production cross sections.
Despite the opposite-sign \osww having a larger total cross section, its EWK-mediated diagrams are much smaller than its QCD-mediated diagrams, while for same-sign \sswwnojj the EWK production is considerably larger.
This makes \ssww one of the premier channels for studying VBS at the LHC.

The first evidence of electroweak (EWK) \ssww production was seen by the ATLAS and CMS experiments at \com{8} with exesses of $3.6\sigma$~\cite{2014.ssww-8tev-atlas} and $2.0\sigma$~\cite{2015-ssww-8tev-cms} over backgrounds, respectively.
More recently, ATLAS and CMS have both observed the EWK process at \com{13} with significances of $6.9\sigma$~\cite{2018.ssww-13tev-atlas-conf} and $5.5\sigma$~\cite{2017.ssww-13tev-cms}, respectively.
The ATLAS \com{13} observation and cross section measurement of EWK-produced \ssww is presented in this chapter~\cite{2018.ssww-13tev-atlas-conf, 2018.ssww-13tev-atlas-support}.

%\section{Analysis Overview}\label{ssww13tev:overview}
\input{sections/ssww_13tev/overview.tex}

\section{Data and Monte Carlo samples}\label{ssww13tev:data_mc}
\input{sections/ssww_13tev/data_mc.tex}

\section{Object and event selection}\label{ssww13tev:object_event_selection}
\input{sections/ssww_13tev/event_selection.tex}

%\section{Signal definition}\label{ssww13tev:signal}
%\input{sections/ssww_13tev/signal.tex}

\section{Background estimations}\label{ssww13tev:background}
\input{sections/ssww_13tev/background.tex}

\section{Cross section measurement}\label{ssww13tev:xsec}
\input{sections/ssww_13tev/xsec.tex}

\section{Summary of uncertainties}\label{ssww13tev:uncertainty}
\input{sections/ssww_13tev/uncertainty.tex}

\section{Results}\label{ssww13tev:results}
\input{sections/ssww_13tev/results.tex}
